---
title: "Bigram and Biterm topic model"
author: "GV"
date: "2024-10-31"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Content 

This page was created for providing the code, reproducing the results and presenting the step-by-step process of the results found in the paper: 

> Valença, G.; Hook, H. Why do some American fear "15-minute cities"?. Paper currently submitted for revision. 

### Import libraries

```{r message=FALSE, warning=FALSE}
library(tm)
library(NLP)
library(stringr)
library(topicmodels)
library(tidytext)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(SnowballC)
library(textstem)
library(reshape2)
library(readxl)
library(stringr)
library(quanteda)
library(igraph)
library(ggraph)
library(tidyverse)
library(tidyr)
library(broom)
```
  
### 1. Import Dataset

```{r message=FALSE, warning=FALSE}
data <- read_xlsx("Reddit_15mincity_Treated_Pass1.xlsx")
```

#### Filter eligible comments from the database 

```{r}
df <- data.frame(data) |>
  filter(Filter == 1) |>   #filter by the comments that were classified as relevant
  select(comment)
```

### 2. Preprocessing
#### Normalize all the terms of the 15-minute city to "15mincity"

```{r}

df$comment <- str_replace_all(df$comment, "15 minute city", "15mincity")
df$comment <- str_replace_all(df$comment, "15 minute city", "15mincity")
df$comment <- str_replace_all(df$comment, "15-minute city", "15mincity")
df$comment <- str_replace_all(df$comment, "15-minute city", "15mincity")
df$comment <- str_replace_all(df$comment, "15-minute cities", "15mincity")
df$comment <- str_replace_all(df$comment, "15 min city", "15mincity")
df$comment <- str_replace_all(df$comment, "15 min cities", "15mincity")
```

#### Standard preprocessing 
```{r}
#Remove punctuation
text2 <- gsub(pattern = "\\W", replace = " ", df)
#Take out urls
text3 <- str_replace_all(text2, "(http\\S+)", "")
#Lowercase words
text4 <- tolower(text3)
#remove single words 
text5 <- gsub(pattern = "\\b[A-z]\\b{1}", replace = " ", text4) 
#Remove whitespace
text6 <- stripWhitespace(text5)
#Lematize terms in its dictionary form
text7 <- lemmatize_strings(text6, dictionary = lexicon::hash_lemmas)

```

#### Remove specific stopwords for bigrams
```{r}
adicional_stopwords <- c("don", stopwords("en"))
text_bigram <- removeWords(text7, adicional_stopwords)
```

### 3. Bigrams

#### Create dataframe

```{r}
df_corpus <- data.frame(text_bigram)
```

#### Create bigram database by separating words in sequences of 2. 

```{r}
bigrams_df <- df_corpus %>%
  unnest_tokens(output = bigram,
                input = text_bigram,
                token = "ngrams",
                n = 2)
```

#### Count the number of bigrams

```{r}
bigrams_df %>%
  count(bigram, sort = TRUE)

btm <- bigrams_df %>%
  count(bigram, sort = TRUE)
```

#Remove stopwords in case it wasn't in the beginning.
#data("stop_words") 

#Separate words into two columns

```{r}
bigrams_separated <- bigrams_df %>%
  separate(bigram, c("word1", "word2"), sep = " ")
```

#Remove stopwords

```{r}
bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)
```


#Count the number of times two words are always together

```{r}
bigram_counts <- bigrams_filtered %>%
  count(word1, word2, sort = TRUE)
```

#Create network of bigrams

```{r}
bigram_network <- bigram_counts %>%
  filter(n > 11) %>% #filter for the most common combinations of bigrams that appear at least 15 times.
  graph_from_data_frame()

set.seed(2016)

a <- grid::arrow(type = "closed", length = unit(.06, "inches"))

ggraph(bigram_network, layout = "fr") +   
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.03, 'inches')) +
  geom_node_point(color = "orange", size = 1) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 0.3, size = 3) +
  theme_void()
```


# Create biterm topic model

```{r}
library(data.table)
library(udpipe)
library(dplyr)
library(BTM)
```

#Arrange document to format required for the udpipe 

```{r}
df_tm <- mutate(df, doc_id =row_number())

colnames(df_tm) <- c("text", "doc_id")

df_tm <- df_tm |> 
  relocate(doc_id, text)
```

#Data cleaning

#Remove punctuation

```{r}
df_tm$text <- gsub(pattern = "\\W", replace = " ", df_tm$text)
```

#Take out urls

```{r}
df_tm$text <- str_replace_all(df_tm$text, "(http\\S+)", "")
```

#Lowercase words

```{r}
df_tm$text <- tolower(df_tm$text)
```

#remove single words 

```{r}
df_tm$text <- gsub(pattern = "\\b[A-z]\\b{1}", replace = " ", df_tm$text) 
```

#Lematize terms in its dictionary form

```{r}
df_tm$text <- lemmatize_strings(df_tm$text, dictionary = lexicon::hash_lemmas)
```

#remove stopwords

```{r}
adicional_stopwords <- c("don, wasn", stopwords("en"))
df_tm$text <- removeWords(df_tm$text, adicional_stopwords)

df_tm$text <- str_replace_all(df_tm$text, "15 minute city", "15mincity")
df_tm$text <- str_replace_all(df_tm$text, "15 minute city", "15mincity")
df_tm$text <- str_replace_all(df_tm$text, "15-minute city", "15mincity")
df_tm$text <- str_replace_all(df_tm$text, "15-minute city", "15mincity")
df_tm$text <- str_replace_all(df_tm$text, "15-minute cities", "15mincity")
df_tm$text <- str_replace_all(df_tm$text, "15 min city", "15mincity")
df_tm$text <- str_replace_all(df_tm$text, "15 min cities", "15mincity")
```

#Remove whitespace

```{r}
df_tm$text <- stripWhitespace(df_tm$text)

```

```{r}
biterm_data_tm <- udpipe(df_tm, "english", trace = 10)
biterms <- as.data.table(biterm_data_tm)
biterms <- biterms[, cooccurrence(x = lemma,
                                  relevant = upos %in% c("NOUN",
                                                         "ADJ",
                                                         "PROPN") & 
                                    !lemma %in% stopwords("en"),
                                  skipgram = 5),
                   by = list(doc_id)]
```


# Build BTM

```{r}
set.seed(588)
traindata <- subset(biterm_data_tm, upos %in% c("NOUN", "ADJ", "PROPN"))
traindata <- traindata[, c("doc_id", "lemma")]
model <- BTM(traindata, k = 5, 
             beta = 0.01, 
             iter = 1000,
             window = 15,
             biterms = biterms, 
             trace = 100)
```

## Inspect the model - topic frequency + conditional term probabilities

```{r}
model$theta

topicterms <- terms(model, top_n = 25)
topicterms <- data.frame(topicterms)
```

#plot topicterms

```{r}
library(textplot)
library(ggraph)
library(concaveman)
plot(model, top_n = 20, title ="",
     labels = paste(round(model$theta *
                            100, 2), "%", sep = ""))

plot(model, top_n = 25, title ="",
     labels = c("Freedom of movement (10.22 %)", "Urban transition (21.41 %)", "Choice and opportunity (38.29 %)", "Explanation (13.43 %)", "Apprehension and misinformation (16.65 %)"))

model$theta
```